\section{Competition}

The competition presents the culmination of the week as teams compete in the Arena against the other teams.

\subsection{Arena build}

The cube needs to be prepared for the competition, this will take the majority of the week.
Documentation on the arena build for the cube can be found in the \dots document.

\task{Arrange for estates to move arena parts to the cube}
\task{Purchace arena construction materials}
\task{Hire scaffolding for arena}
\task{Book tables and chairs from SUSU}
\task{Book tech from SUSU}
\task{Find arena screens}
\task{Plan arena lighting schedule}
\task{Print marker and signge}

\subsection{Tinker time}

Thursday afternoon and early, Friday morning, and during breaks is used for tinker time where teams can test their robots in the arena.
During this time a volunteer will manage slots for teams to come into the arena and test.
Timeslots are booked on a whiteboard and the PA system is used to announce the slots.

\subsection{Competition briefing}

On Friday morning the Head Judge will give the competition briefing explaining how the league will work.

\subsection{Friday break closure}

During the Friday morning break the cube is closed to allow for the arena to be converted into competition mode and any last minute tests to be run.
At this point the house lights are turned off and the arena lighting setup is turned on.
The music is also swapped to the epic playlist and the preselected intro song is started at which point he competitors' are invited back into the arena ready for the first match.

\task{Plan competition intro sequence}

\subsection{League}

\task{Prepare league schedule}

\subsection{Knockouts}

\task{Prepare knockout schedule}

\subsection{Prize giving}

\task{Purchase prizes}
\task{Design certificates}
\task{Design awards cards}
\task{Print awards cards and certificates}
\task{Prepare post competition schedule}
\task{Find speaker for post finals talk}
\task{Book awards speaker}
