\section{Initial planning}

The initial planning for the summer school happens in around October/November.
At this stage the key tasks are to work out who is doing the organisation and the details of the course in order to open registrations.

\subsection{Key roles allocation}

The key leads in each organisation need to be identified.
Sourcebots needs a representative to manage discussions with ECS and keep track of tasks.
ECS need to select an academic who will be in charge of the course from their end.
Smallpeice will let us know of the course leader from their end.

\task{ECS to select academic lead}
\task{Select primary Sourcebots organisational contact}

\subsection{Create Improvements list for coming year}

At this stage any major improvements to the summerschool should be identified.
The appropriate tasks to implement these changes should be added to this runbook.

\task{Review retrospective to identify improvements}

\subsection{Budget acquisition}

Smallpeice provide the funds for the food, accommodation and evening activities.
The funds required to run the daytime robotics activities come from the university.
In order for ECS to allocate the required funds a draft budget is required.
This budget can be largely worked out from the previous years costs but may require additional planning if changes are planned with new costs.

\task{Perform rough inventory for budgetary planning}
\task{Create a draft budget for ECS budgetary planning}
\task{ECS to confirm budget and provide cost codes}

\subsection{Course definition}

The course details need to be confirmed between ECS Smallpeice and Sourcebots.
A description of the course needs to be created in order to promote the course.
The description can probably be kept from the previous year unless significant changes in content are planned.
In addition the number of students needs to be confirmed.

\task{Confirm course definition.}

\subsection{Date confirmation}

Proposed dates are usually suggested by Smallpeice after discussions with the university Hospitality and catering department.
Before dates can be confirmed there are several key resources that need to be booked.
The most important of these is the Cube where the competition will be held.

\task{Get provisional Cube booking}
\task{Book electronics labs}
\task{Confirm summer school dates with Smallpeice}
