\section{Later stage planning}

Closer to the event there are several planning steps that need to be done.

\subsection{Computing resources}

There are several computing resources that need to be acquired.
Conference accounts are required for the sudents so they can log into the lab computers and use the WiFi.
In addition there needs to be a laptop per team for use in the cube.

\task{Confirm conference accounts}
\task{Borrow laptops}

\subsection{Catering conformations}

Before the event \todo{Insert time} the catering details and bookings need to be confirmed.

\task{Confirm formal meal attendance}
\task{Confirm break catering}
\task{Confirm meal catering}
\task{Book SUSU refreshments}

\subsection{Information pack information}

About a month before the event Smallpeice send out the event information and several pieces of information need to be included in this pack.

\task{Confirm week schedule}
\task{Invite parents to finals}
\task{Book carparking}

\subsection{Rules creation}

The rules for the game will need creating.
This involves the design of the game which should conform to the game design criteria.

\task{Prepare rules Q\&A}
\task{Create rules}
\task{Prepare filming and Photography plan}

\subsection{Risk assesments}

At this stage the risk assessments for the various activities during the week need to be created.

\task{Create Competitor risk assessment}
\task{Create Volunteer risk assessment}

\subsection{Prepare Student packs}

At the introductory talk each student is given a pack.
These bags include printouts of the rules and a map of campus, and prospectuses.
The bags also include the USB sticks they will use when programming the robots.

\task{Print rules documents}
\task{Pack bags of pens etc. for students}
\task{Acquire bags for student packs}
\task{Print maps for student packs}
\task{Acquire prospectuses}
\task{Create kit USB sticks}
\task{Pack team packs}
