\section{Volunteers}

At around April time work to invite and select volunteers from Sourcebots for helping run the summer school is required.
This needs to be done late enough so that those with summer internships know what their status is over the summer.
The number of volunteers required needs to be worked out at this time and the number of volunteers limited to this amount.
Table \ref{tab:volunteerroles} shows the main roles and numbers required for those roles to give an idea of how many volunteers are needed.
In addition to these there will need to be several free volunteers available to assist with other tasks such as running workshops.

\begin{table}
    \centering
    \begin{tabular}{cc}
        Role & Number of volunteers required \\
        \hline
        Organisation lead & 1 \\
        Team mentors & 1 per two teams \\
        Labs Lead & 1 \\
        Workshop supervisors & 2 \\
        Arena build team & 3\\
    \end{tabular}
    \caption{Roles for volunteers during the summer school}
    \label{tab:volunteerroles}
\end{table}

\task{Open signups for volunteers for the summer school}

\subsection{Catering and accommodation}

At around June we will need to confirm to Smallpeice which volunteers require accommodation or have dietary requirements.
To do this we need to work out who is around for what days as we will need a good number of the volunteers on the weekends before and after.
Historically as well as the course days we have been able to get accommodation on the Saturday and Sunday before and the Friday and Saturday afterwards for volunteers who are available then.

\task{Collect accommodation and catering requirements from volunteers}

\subsection{Volunteer briefing}

On the Sunday before the event there will be a briefing for all the volunteers in order to bring everyone up to speed on the plans for the week and what needs to happen.
At the same time any kit being loaned from volunteers should be recorded to make sure it is returned at the end of the event.

\task{Create volunteer roles document}
\task{Brief volunteers}
\task{Create interactive volunteer schedule}
\task{Prepare forms for loaned kit}
